Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-12 main.Rmd
changed the layout of Figure 4 to fix aspect ratio

(ref:bothcust) Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: 1. hour of the day; and 2. weekday/weekend. **a** shows granularity 2 faceted by granularity 1; **b** and **c** shows the reverse mapping. **a** allows comparison of usage by workday within each hour of the day using side-by-side boxplots, showing that on work days there is more consumption early in the day. **b** and **c** examine the temporal trend of consumption over the course of a day, separately for the type of day.**b** uses an area quantile to emphasize the time component; e.g., median consumption shows prolonged high usage in the morning on weekdays. **c** uses a violin plot emphasizes subtler distributional differences across hours, showing that morning use on weekdays is bimodal, and on some work days there is low usage possibly indicating the person is working from home or having a late start.

>>>>

(ref:bothcust) Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: 1. hour of the day; and 2. weekday/weekend. **a** shows granularity 2 faceted by granularity 1; **b** and **c** shows the reverse mapping. **a** allows comparison of usage by workday within each hour of the day using side-by-side boxplots, showing that on work days there is more consumption early in the day. **b** and **c** examine the temporal trend of consumption over the course of a day, separately for the type of day. **b** uses an area quantile to emphasize the time component; e.g., median consumption shows prolonged high usage in the morning on weekdays. **c** uses a violin plot emphasizes subtler distributional differences across hours, showing that morning use on weekdays is bimodal, and on some work days there is low usage possibly indicating the person is working from home or having a late start.
